Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2020-06-11 main.Rmd
edited the number EffectR data predicted by cnn-lstm and EffectR.

We also evaluated the deep learning models we have developed on the training and hold-out validation sequences used to train the previous methods. We calculated accuracy and F1 score of all the tools on their respective training and validation sets, according to availability. The bacterial tools EffectiveT3 and DeepT3 showed lower accuracies and F1 score on all sequence sets tested, than our Ensemble Weighted model, as in Figure \@ref(fig:owndata)A, consistent with the observation that our Ensemble Weighted model performed more strongly on the validation set that we generated. Interestingly, both versions of EffectorP showed greater accuracy and F1 score on the EffectorP provided training sets than our CNN-LSTM model, but in the unseen validation data provided with EffectorP 2, all three models performed identically in both metrics \@ref(fig:owndata)B. The EffectorP 1 and 2 scores on validation data are well below the scores for the training data, a result that is usually interpreted as being evidence of an overfitted and less generalisable model. Our CNN-LSTM model for fungi showed similar scores across the training and validation set indicating a greater generability. Only six effector sequences are provided as examples with the oomycete specific effector finder effectR. As this is not a trainable model in the same sense as the others, no large training set is needed. We attempted classification with these and effectR was able to classify X of the six ^[Ruth, can you add the actual numbers of classified for this one], whereas our CNN-LSTM model for oomycetes classified  Y of the six\ref(fig:owndata)C.

>>>>

We also evaluated the deep learning models we have developed on the training and hold-out validation sequences used to train the previous methods. We calculated accuracy and F1 score of all the tools on their respective training and validation sets, according to availability. The bacterial tools EffectiveT3 and DeepT3 showed lower accuracies and F1 score on all sequence sets tested, than our Ensemble Weighted model, as in Figure \@ref(fig:owndata)A, consistent with the observation that our Ensemble Weighted model performed more strongly on the validation set that we generated. Interestingly, both versions of EffectorP showed greater accuracy and F1 score on the EffectorP provided training sets than our CNN-LSTM model, but in the unseen validation data provided with EffectorP 2, all three models performed identically in both metrics \@ref(fig:owndata)B. The EffectorP 1 and 2 scores on validation data are well below the scores for the training data, a result that is usually interpreted as being evidence of an overfitted and less generalisable model. Our CNN-LSTM model for fungi showed similar scores across the training and validation set indicating a greater generability. Only six effector sequences are provided as examples with the oomycete specific effector finder effectR. As this is not a trainable model in the same sense as the others, no large training set is needed. We attempted classification with these and effectR was able to classify 12 of the 14, whereas our CNN-LSTM model for oomycetes classified nine of the 14, see Figure \@ref(fig:owndata)C.
